Proposal for Analyzing Language Models: Separatablity of Syntax and Semantics

### 2022-06-09 paper/paper.tex
Data section added - needs work
Added the data section with some info about the parallel meaning bank, but was unable to find all relevant info on the sites provided and unable to load the data on my end, so I need someone else to check this and fill in the missing info if possible.

%Description of the data set used and the information it contains relevant to the tasks of interest. Talk about pre-processing the syntax trees to get CCG tags. 
%We will use the English V4 subset of the CoNLL 2012 shared task data \citep{2012-conll} . We must perform two pre-processing steps for this data to be used for our probing and evaluation tasks. The first is to apply \citet{ccg-bank}'s CCG Derivation algorithm to the parse tree field in the dataset, in order to create the CCG tags for each word. If this proves to be too time-consuming or computationally expensive then we shall change the syntactic probing task to utilize the POS tags available in the dataset, in place of CCG tags. The second task is to use the SRL frames in the dataset to generate (verb, BIO-argument-tag) pairs that will act as the categories for the semantic probing task.

%Need to update this section to reflect the new dataset
We use the NAME data set to test the linear separability of the semantic and syntactic information in word-level BERT embeddings. %NEED TO FILL THIS OUT STILL

>>>>

%Need to update this section to reflect the new dataset
We use the English gold standard of Parallel Meaning Bank v4.0 \citep{pmbData} to test the linear separability of the semantic and syntactic information in word-level BERT embeddings. This data set contains word-level semantic tags and NAME FEATURE USED FOR CCG DERIVATIONS %Fill this in
 that we parse using CITE CCG PARSER %Fill this in
 to develop word-level CCG tags, both of which are used to train the linear classifiers used for probing and evaluation. The gold-standard data set is comprised of XX words. %Fill this in
 %Do we drop anything or do any other pre-processing that I missed here?
